The problem and promise of scale in multilayer networks

### 2020-02-03 paper/manuscript.Rmd
edits metrics

### Network metrics
We used a series of metrics to characterize the multilayer networks, focusing on
the the role of individuals and the similarity and relevance of individual layers. Degree
centrality, the number of direct connections an individual has to other individuals in the
network, is the basis of many calculations. We calculated multidegree, the sum of degree
centrality across layers, and neighbourhood, the sum of unique neighbours to each
individual[@Berlingerio_2012; @Kivela_2014]. Comparing the multidegree and number of
unique neighbours, we measured the connective redundancy, the proportion of
neighbours repeated in multiple layers, and the layer relevance, the proportion
of neighbours present compared to the neighbourhood for each individual
[@Berlingerio_2012]. To measure the role of individuals, we calculated the graph
strength, degree weighted by the values of the tie, for each individual for each 
layer-specific season and landcover context <!-- citation?-->. Finally, we calculated the 
similarity of layers between seasons, across landcover classes (e.g.: winter open compared 
to summer open) using the Pearson correlation coefficient [@Br_dka_2018].

>>>>

### Network metrics
We used a series of metrics to characterize the multilayer networks, focusing on
the the role of individuals, relevance of individual layers and the similarity
of different layers. To measure the role of individuals, we calculated the graph
strength, degree weighted by the values of the edge, for each individual for
each layer-specific season and landcover context <!-- TODO: citation for graph
strength?-->. Degree centrality, the number of direct connections an individual
has to other individuals in the network, is the basis of many calculations
[@Kivela_2014]. We calculated multidegree, the sum of degree centrality across
layers, and neighbourhood, the sum of unique neighbours to each individual
[@Berlingerio_2012; @Kivela_2014]. Comparing the multidegree and neighbourhood,
we measured the connective redundancy, the proportion of neighbours repeated in
multiple layers, and the layer relevance, the proportion of neighbours present
in each layer compared to the neighbourhood for each individual
[@Berlingerio_2012].  Finally, we calculated the similarity of layers between
seasons, across landcover classes (e.g.: winter open compared to summer open)
using the Pearson correlation coefficient [@Br_dka_2018].
